Structure Learning for $\VAR(p)$ Models

### 2019-05-31 paper/paper.tex
Working on statistical tests for pairwise GC.

>>>>

\section{Finite Sample Graph Recovery}
\label{sec:structure_learning}
\hl{TODO: Citation for this scheme}
In performing pairwise estimates $x_j \pwgc x_i$ we follow the simple
scheme of estimating the following two linear models via ordinary
least squares:

\begin{align}
  H_0:&\ \widehat{x}_i^{(i)}(t) = \sum_{\tau = 1}^{p_i} b_{ii}(\tau)x_i(t - \tau),\\
  H_1:&\ \widehat{x}_i^{(i, j)}(t) = \sum_{\tau = 1}^{p_i} b_{ii}(\tau)x_i(t - \tau) + \sum_{\tau = 1}^{p_j}b_{ij}(\tau)x_j(t - \tau).
\end{align}

Under the null hypothesis $H_0$ we can form the asymptotically
$\chi^2(p_j)$ distributed test statistic

\begin{equation}
  F_{ij} = \frac{T}{p_j}\Big(\frac{\xi_i}{\xi_{ij}} - 1\Big),
\end{equation}

where $\xi_i$ is the sample mean square of the residuals $x_i(t) - \widehat{x}^{(i)}_i(t)$, and similarly for $\xi_{ij}$.  Given additional assumptions on $x(t)$ (\hl{TODO: What assumptions?}) we have the convergence (\hl{a.s. or in P?})

\begin{equation}
  \underset{T \rightarrow \infty}{\text{lim }}F_{ij} =
  \left\{
    \begin{array}{ll}
      0;\ x_j \npwgc x_i\\
      \infty;\ x_j \pwgc x_i
    \end{array}
  \right.
\end{equation}

Therefore, we can make the statement that Algorithm \ref{alg:pwgr_heuristic} asymptotically implements Algorithm \ref{alg:pwgr}.  \hl{TODO: Modify Algorithm 2 to make this true.}

It is known (\hl{citation}) that $F_{ij}$ is sensitive to the choice of $p_i$ and $p_j$.
